An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-21 VLDB2026/main.tex
change

	In recent years, hybrid query algorithms develop rapidly, giving rise to numerous attribute filtering ~\cite{NHQ,diskann} and range filtering algorithms \cite{serf,iRangeGraph}. In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely related to structured data. For attribute filtering algorithms, factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute  selectivity \textcolor{orange}{\cite{analyticdb,milvus}} significantly impact algorithm performance. As for range filtering algorithms, the size of the query range and the characteristics of different datasets  play an important role in determining algorithm performance.

@@

	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015}, covering a diverse range of domains. We independently generate attribute for each dataset.
	For range filtering queries, we evaluate 3 widely used real-world datasets: Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and WIT~\cite{wit_dataset}. Following prior work~\cite{DSG}, we use the data point ID within each dataset as its attribute. This ensures that the data is initially sorted.

@@

		\label{tab:datasets_combined}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{cccccc}
				\toprule
				Dataset & Dimension & Base Data & Queries & LID & Type \\
				\midrule
				Msong & 420 & 992,272 & 200 & 23& Audio \\
				Audio & 192 & 53,387 & 200 & 14& Audio \\
				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image \\
				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image \\
				GloVe & 100 & 1,183,514 & 10,000 & 47& Text \\
				Enron & 1369 & 94,987 & 200 & 23& Text \\
				Deep & 96 & 1,000,000 & 10,000 & 22& Image \\
				YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image \\
				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image \\
				Text2Image-Mix & 200 & 10,000,000 &10,000 & 59& Text,Image \\
				\bottomrule
			\end{tabular}
		}
	\end{table}

>>>>

	In recent years, hybrid query algorithms develop rapidly, giving rise to numerous attribute filtering ~\cite{NHQ,diskann} and range filtering algorithms \cite{serf,iRangeGraph}. In practical applications, the performance of hybrid query algorithms is influenced not only by unstructured data but also closely related to structured data. For attribute filtering algorithms, factors such as the number of attributes, attribute distribution \cite{UNG}, and attribute selectivity \cite{ACORN} significantly impact algorithm performance. As for range filtering algorithms, the size of the query range and the characteristics of different datasets  play an important role in determining algorithm performance.

@@

	For attribute filtering tasks, we employ 6 real-world datasets widely adopted in existing literature: Msong~\cite{msong2011}, Audio~\cite{audio_unknown}, SIFT1M~\cite{sift2010}, GIST1M~\cite{sift2010}, GloVe~\cite{GloVe2015}, Enron~\cite{enron2015}, covering a diverse range of domains. We independently generate attribute for each dataset.
	For range filtering queries, \textcolor{red}{we evaluate 1 widely used real-world dataset: %Deep~\cite{yandex_deep_dataset}, YT-Audio~\cite{youtube8m_dataset}, and 
	WIT~\cite{wit_dataset}. Following prior work~\cite{DSG}, we use the data point ID (the primary key, ranging from $0$ to $n-1$) within each dataset as its attribute. This ensures that the data is initially sorted.}

@@

		\label{tab:datasets_combined}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{cccccc}
				\toprule
				Dataset & Dimension & Base Data & Queries & LID & Type \\
				\midrule
				Msong & 420 & 992,272 & 200 & 23& Audio \\
				Audio & 192 & 53,387 & 200 & 14& Audio \\
				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image \\
				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image \\
				GloVe & 100 & 1,183,514 & 10,000 & 47& Text \\
				Enron & 1369 & 94,987 & 200 & 23& Text \\
				%Deep & 96 & 1,000,000 & 10,000 & 22& Image \\
				%YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\
				YT-Audio-Real& 128 & 1,000,000 & 10,000 & 15& Audio \\
				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\
				WIT-Real & 512 & 1,000,000 & 40,300 & 48& Image \\
				Text2Image & 200 & 10,000,000 &10,000 & 59& Text,Image \\
				Text2Image-Mix & 200 & 1,000,000 &10,000 & 59& Text,Image \\
				Deep100M & 96 & 100,000,000 & 10,000 & 22& Image \\
				\bottomrule
			\end{tabular}
		}
	\end{table}
